---
title: "Graph Replication"
subtitle: "Week 4 Activity"
author: ""
date: ""
output: 
  html_notebook:
    fig_height: 3
    fig_width: 5
---

```{r}
# libraries
library(magrittr)
library(mosaic)
library(mosaicData)
library(manipulate)
library(esquisse)
library(ggplot2)
library(ggthemes)
library(dcData)
```


# Grading

Assignment is worth a total of 10 points:

- [3 points] Problem 5.2 graph replication  
- [3 points] Problem 5.3 graph replication   
- Exploration of `diamonds` data  
    - [1 point] `ggplot2` expression that successfully produces a graphical display of the `diamonds` data.  
    - [1 point] graphic must display at least 3 variables from the `diamonds` data.  
    - [2 points] written narrative describing something learned/observed about the `diamonds` data using your graphic.  

# Activity

Reproduce plots for Problem 5.2 & Problem 5.3 in the Data Computing Text.

___

###  Problem 5.2

The "yes" and "no" in the gray bars refer to whether or not the person is pregnant.


```{r}
ggplot(NCHS) +
 aes(x = bmi, colour = sex) +
 geom_density() +
 scale_color_hue(direction = 1) +
 theme_minimal() +
 facet_wrap(vars(pregnant))
```


___

###  Problem 5.3
```{r}
ggplot(data = CPS85, aes(x = exper, y = wage)) + geom_point()  + aes(colour = married) + scale_x_log10() + scale_y_log10() + facet_wrap(~sector, ncol = 4) + theme(legend.position = "right") + labs(title = "")
```

___

### Your Turn: explore the `diamonds` data

*Task: Produce an interesting graphic of the `diamonds` data set.  The graphic should represent AT LEAST 3 variables.  Write a few sentences to describe what you have learned. Remember that the esquisser() function will not work in a markdown document. You must create the plot using the console and then copy the expression into this assignment.*

```{r}
ggplot(data = diamonds, aes(x = carat, y = price)) +
geom_point() + aes(color = clarity) +
scale_color_hue(direction = 1) +
theme_minimal()
```

___


### Optional Extension: programming style

The helper functions are great, but they produce ugly code.  Clean up the `ggplot2` code that reproduces the required plots so that it aligns with the R Programming Style Guide Appendix in the *DataComputing* eBook <https://dtkaplan.github.io/DataComputingEbook/>.  
